Accelerated Magnetic Resonance Imaging by Adversarial Neural Network

### 2018-01-16 paper.tex
Update with tammy

We introduce a practical, software-only framework, based on deep learning, for accelerating MRI scan time allows maintaining good quality imaging. This is accomplished by partial MRI sampling, while using an adversarial neural network to estimate the missing samples. The inter-play between the generator and the discriminator networks enables the introduction of an adversarial cost in addition to a fidelity loss used for optimizing the peak signal-to-noise ratio (PSNR). Promising image reconstruction results are obtained for 3T and 1.5T MRI where only 40\%, 25\% and 16.6\% of the original data are used. Extended performance assessment was conducted in order to emphasize the advantage of proposed method.
\end{abstract}

\begin{keyword}
\texttt MRI \sep GAN \sep Accelerated \sep K-space
%\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

The compressed sensing (CS) technique~\cite{donoho2006compressed} allows efficient acquisition and reconstruction of a signal with fewer samples than the Nyquist-Shannon sampling theorem requires, if the signal has sparse representation in a known transform domain. Using CS for MRI reconstruction by sampling a small subset of the k-space grid had been proposed in~\cite{lustig2007sparse}. The underlying assumption is that the undersampling is random, such that the zero-filled Fourier reconstruction exhibits incoherent artifacts that behave similarly to additive random noise. {\color{red}This, however, makes the algorithm less sensitive to fine details and noise like texture, results in smooth reconstruction with loss of diagnostically information, as we will see in section \ref{experiments_section}.}
%This, however, would require specified pulse programming.

Recently machine learning techniques based on manifold learning~\cite{usman2014compressive,bhatia2015fast} and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary} were suggested for MRI reconstruction. MRI reconstruction using convolutional neural networks (CNN) was introduced in \cite{wang2016accelerating}. The network learns the mapping between zero-filled and fully-sampled MR images. In \cite{Oktay2016}, residual network was proposed for MRI super-resolution. Their model is able to receive multiple inputs acquired from different viewing planes for better image reconstruction. In \cite{lee2017deep,hyun2017deep} a multi-scale residual network, also known as U-net~\cite{ronneberger2015u} is used and provides good reconstruction MR images.
Deep convolutional networks have been successfully applied to acceleration of dynamic MRI in \cite{sandinodeep}. All these works address the reconstruction problem in the image domain rather than the k-space domain.

>>>>

We introduce a practical, software-only framework, based on deep learning, for accelerating MRI acquisition, while maintaining anatomically meaningful imaging. This is accomplished by partial MRI sampling, while using an adversarial neural network to directly estimate the missing k-space samples. The inter-play between the generator and the discriminator networks enables the introduction of an adversarial cost in addition to a fidelity loss used for optimizing the peak signal-to-noise ratio (PSNR). Promising image reconstruction results are obtained for 3T and 1.5T brain MRI, from large publicly available dataset, where only 40\%, 25\% and 16.6\% of the raw samples of each scan are used. To assess the clinical usability of the reconstructed images we also performed tissue segmentation and compared the results to those obtained by using the original fully-sampled images.
Segmentation compatibility, measured in terms of Dice scores and Hausdorff distances, demonstrate quality of the proposed MRI reconstruction with respect to other methods, including the widely-used Compressed Sensing.

\end{abstract}

\begin{keyword}
\text Accelerated MRI \sep Adversarial Loss \sep Deep Neural Network \sep K-space
%\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

The compressed sensing (CS) technique~\cite{donoho2006compressed} allows efficient acquisition and reconstruction of a signal with fewer samples than the Nyquist-Shannon sampling theorem requires, if the signal has sparse representation in a known transform domain. Using CS for MRI reconstruction by sampling a small subset of the k-space grid had been proposed in~\cite{lustig2007sparse}. The underlying assumption is that the undersampling is random, such that the zero-filled Fourier reconstruction exhibits incoherent artifacts that behave similarly to additive random noise. 
The smooth reconstruction obtained by the CS, may result in a loss of noise-like texture that can be anatomically meaningful.

%{\color{red}This, however, makes the algorithm less sensitive to fine details and noise like texture, results in smooth reconstruction with loss of diagnostically information, as we will see in section \ref{experiments_section}.}
%This, however, would require specified pulse programming.

Recently machine learning techniques based on manifold learning~\cite{usman2014compressive,bhatia2015fast} and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary} were suggested for MRI reconstruction. MRI reconstruction using convolutional neural networks (CNN) which learns the mapping between zero-filled and fully-sampled MR images was introduced in \cite{wang2016accelerating}. In \cite{Oktay2016}, residual network was proposed for MRI super-resolution. Their model is able to receive multiple inputs acquired from different viewing planes for better image reconstruction. In \cite{lee2017deep,hyun2017deep} a multi-scale residual network, also known as U-net~\cite{ronneberger2015u} is used and provides good reconstruction MR images.
Deep convolutional networks have been successfully applied to acceleration of dynamic MRI in \cite{sandinodeep}. All these works address the reconstruction problem in the image domain rather than the k-space domain.
